### 2023-02-02 README.qmd
updated README

---
format: commonmark
---

@@

This repository contains all code, notebooks, data and empirical results for our conference paper "Endogenous Macrodynamics in Algorithmic Recourse". Below is a list of relevant resources hosted in this repository:

1. [Paper](paper/paper.pdf)
2. [Online Companion](https://www.paltmeyer.com/endogenous-macrodynamics-in-algorithmic-recourse/)
3. [IEEE SaTML Presentation Slides](https://www.paltmeyer.com/content/talks/posts/2023-ieee-satml/presentation.html)
4. [IEEE SaTML Poster](dev/poster/poster.pdf)

@@

>>>>

---
format: commonmark
bibliography: bib.bib
---

@@

This repository contains all code, notebooks, data and empirical results for our conference paper "Endogenous Macrodynamics in Algorithmic Recourse" [@altmeyer2023endogenous].

Below is a list of relevant resources hosted in this repository:

1. [Paper](paper/paper.pdf) in this repo 
2. [Paper](https://openreview.net/pdf?id=-LFT2YicI9v) on OpenReview
3. [Online Companion](https://www.paltmeyer.com/endogenous-macrodynamics-in-algorithmic-recourse/)
4. [IEEE SaTML Presentation Slides](https://www.paltmeyer.com/content/talks/posts/2023-ieee-satml/presentation.html)
5. [IEEE SaTML Poster](dev/poster/poster.pdf)
6. Software: [`AlgorithmicRecourseDynamics.jl`](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl) and [`CounterfactualExplanations.jl`](https://github.com/pat-alt/CounterfactualExplanations.jl)

@@

## References
